Experience shapes individual foraging specialization and success in a virtual predator-prey system

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
added notes for par 2 and 3

Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g. search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015]. Through this process, predators with extensive practice acquire expertise (e.g. skills, knowledge) that allows them to outperform novice hunters [@Dukas2019]. In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g. repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019]. Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility. For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013]. To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].

@@

However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e. specialization and flexibility) operating at the same time within a predator population. For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022]. Thus, it should be essential for predators to learn how to adjust their tactic to their prey to optimize their success.

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017]. Some studies have found greater success for individuals specializing on a foraging tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021]. This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility. However, many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018]. It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010]. While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how. Given the dynamic nature of predator-prey interactions, it is likely that ontogenic behavioural changes in predators play an important role, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].

>>>>

Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g. search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015]. Through this process, predators with extensive practice acquire expertise (e.g. skills, knowledge) that allows them to outperform novice hunters [@Dukas2019]. In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g. repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019]. Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility. For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013]. To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013]. The importance of context in defining how individual predators learn to hunt makes it difficult to predict whether they should specialize or not in their foraging behaviour with experience.

@@

However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e. specialization and flexibility) operating at the same time within a predator population. For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].

Deux idées pour le paragraphe suivant :
1. Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
2. soit focus sur le fait qu'il y a des différences d'aptitude

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017]. Some studies have found greater success for individuals specializing on a foraging tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021]. This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility. However, 
(*pourrait retirer en haut et commencer ici*)
many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018]. It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010]. While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how. Given the dynamic nature of predator-prey interactions, it is likely that ontogenic behavioural changes in predators play an important role, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
